Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-07 Manuscript/manuscript.tex
Written section validation of membrane properties

\subsection{Validation of membrane properties} 
\todo{SAMULI: I would put under under this section.
1) a very short explanation of the usage of electrometer concept in this paper by mainly citing NMRlipids IV.
2) a very short explanation of the usage of form factor and order parameters by citing approriate publications}

The structures of lipid bilayers in simulations without ions were validated against NMR by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating the scattering form factors. 
NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
The simulated order parameters were calculated for all C-H bonds in lipid molecules from Eq. \ref{OP}.
Scattering form factors validate the dimensions of the lipid bilayer (i.e., the bilayer thickness and area per molecule). Form factors were calculated using a relation

\begin{equation} 
  F(q) = \int _{-D/2} ^{D/2} \left ( \rho_{el}(z) - \rho_{el}^s \right ) \cos (zq_z) \mathrm{d}z, 
  %F(q) = \int _{-D/2} ^{D/2} \left ( \sum _\alpha f_\alpha (q_z) n_\alpha (z) - \rho _s \right ) \exp (izq_z) \mathrm{d}z, 
\end{equation}

\noindent where $\rho_{el} (z)$ is the total electron density, $\rho_{el}^s$ is the electron density of the solvent far in the aqueous bulk, and $z$ is the distance from the membrane center along its normal with $D/2$ being half of the unit cell size.

@@

We compared X-ray scattering form factors and NMR order parameters of bilayers
in pure water without any ions (or only counter ions)
from simulations and experiments
as the first step in the assessment of the quality of the model. 
The experimental X-ray scattering form factors 
of a bilayer are well reproduced for all lipids employing the presented ECC-lipids model 
(see Figs.~\ref{fig:simVSexpNOions}, \ref{simVSexpNOions_POPE} and \ref{simVSexpNOions_POPS}).

>>>>

\subsection{Validation of membrane properties}

The structures of lipid bilayers in simulations without ions were validated against NMR 
by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating the scattering form factors
as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
(see next section and Fig.~\ref{simVSexpNOions_POPS}).

Ion binding to lipid bilayers can be experimentally quantified
by measuring the changes of the head group order parameters in the lipids using solid state NMR.
In the case of the head group order parameters $S^\alpha$ and $S^\beta$ in phosphatidylcholine
(see Fig.~\ref{simVSexpNOions_POPS} for the definition of the order parameters)
such changes are known under the term ''electrometer concept'' \citep{seelig87,catte16, ollila16, melcr18, nmrlipids_proj4}. 
It is experimentally observed that the \ce{C-H} bond
order parameters of $S^\alpha$ and $S^\beta$ carbons in a PC lipid head group
are proportional to the amount of charge, positive or negative, bound per lipid~\citep{seelig87, roux90}.
The change of the order parameters measured with varying concentrations of aqueous ions 
can be then related to the amount of bound ions.

@@

We compared X-ray scattering form factors and NMR order parameters of bilayers
in pure water without any ions (or only counter ions)
from simulations and experiments
as the first step in the assessment of the quality of the model. 
The experimental X-ray scattering form factors 
of a bilayer are well reproduced  
(see Fig.~\ref{simVSexpNOions_POPS}).
